Weight analysis

### 2023-04-24 code/weight_analyses/weight_analysis.Rmd
Update weight_analysis.Rmd
Added here() for relative path building

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rstatix)
library(ggpubr)
library(patchwork)
library(tidyverse)
library(readxl)
library(broom)
```

#___Analysis of the weight development in the MARTRINEM study___
```{r}
data <- read_excel("data/processed/weight_development.xlsx") %>% 
  select(sample_id:cage, bodyweight_birthday_group_average, bodyweight_birthday_plus_24H_group_average, bodyweight_birthday_plus_48H_group_average, bodyweight_baseline, bodyweight_baseline_plus_24h, bodyweight_baseline_plus_48h) %>% 
  rename(day_0 = "bodyweight_birthday_group_average",
         day_1 = "bodyweight_birthday_plus_24H_group_average", 
         day_2 = "bodyweight_birthday_plus_48H_group_average",
         day_3 = bodyweight_baseline, 
         day_4 = `bodyweight_baseline_plus_24h`, 
         day_5 = `bodyweight_baseline_plus_48h`,) %>% 
  pivot_longer(., cols = c(day_0:day_5),
                names_to = "time",
                values_to = "bodyweight") %>% 
  mutate(received_antibiotics = recode_factor(received_antibiotics, 
                                       Yes = "MAT",
                                       No = "CON"))
  #%>%
  # #mutate(across(where(is_character),as_factor))
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rstatix)
library(ggpubr)
library(patchwork)
library(tidyverse)
library(readxl)
library(broom)
library(here)
```

#___Analysis of the weight development in the MARTRINEM study___
```{r}
data <- read_excel(here("data", "processed","weight_development.xlsx")) %>% 
  select(sample_id:cage, bodyweight_birthday_group_average, bodyweight_birthday_plus_24H_group_average, bodyweight_birthday_plus_48H_group_average, bodyweight_baseline, bodyweight_baseline_plus_24h, bodyweight_baseline_plus_48h) %>% 
  rename(day_0 = "bodyweight_birthday_group_average",
         day_1 = "bodyweight_birthday_plus_24H_group_average", 
         day_2 = "bodyweight_birthday_plus_48H_group_average",
         day_3 = bodyweight_baseline, 
         day_4 = `bodyweight_baseline_plus_24h`, 
         day_5 = `bodyweight_baseline_plus_48h`,) %>% 
  pivot_longer(., cols = c(day_0:day_5),
                names_to = "time",
                values_to = "bodyweight") %>% 
  mutate(received_antibiotics = recode_factor(received_antibiotics, 
                                       Yes = "MAT",
                                       No = "CON"))
  #%>%
  # #mutate(across(where(is_character),as_factor))
```
